`r if (knitr:::is_html_output()) '
# Referències {-}
'`



Holi

## math example

a math equation $a^2 + b^2 = c^2$.

$p$ is unknown but expected to be around 1/3. Standard error will be approximated

$$
SE = \sqrt(\frac{p(1-p)}{n}) \approx \sqrt{\frac{1/3 (1 - 1/3)} {300}} = 0.027
$$

You can also use math in footnotes like this^[where we mention $p = \frac{a}{b}$].

We will approximate standard error to 0.027[^longnote]

[^longnote]: $p$ is unknown but expected to be around 1/3. Standard error will be approximated

    $$
    SE = \sqrt(\frac{p(1-p)}{n}) \approx \sqrt{\frac{1/3 (1 - 1/3)} {300}} = 0.027
    $$







```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```
